---
title: "Diagnose Flux Issues from 2013"
author: "Marguerite Mauritz"
date: '2022-11-09'
output: html_document
---

```{r setup, include=FALSE}
# load libraries
library(ggplot2) # library for making figures in ggplot package
library(lubridate) # library for easier date manipulation 
library(data.table) # library for data table which is more efficient with large data sets
library(dplyr)
library(cowplot)
```

## Import data
```{r cars, include=FALSE, echo=FALSE}
# EddyPro 7.0.4 has column name slip problems, using Fluxnet output!

# read the data in fluxnet format

flux2013 <- fread("~/Desktop/TweedieLab/Projects/Jornada/EddyCovariance/JER_Out_2013/eddypro_JER_2013_fluxnet_2019-08-08T105511_adv.csv",
                  sep=",", header=TRUE, na.strings=c("-9999"))

# remove duplicate data
flux2013 <- (flux2013[!(duplicated(flux2013, by=c("TIMESTAMP_START")))])

# make sure the data are ordered:
flux2013 <- flux2013[order(TIMESTAMP_START),]

# format date
flux2013[,':=' (date_time_orig = parse_date_time(TIMESTAMP_END,"YmdHM",tz="UTC"))][
  ,':='(date_orig=as.Date.POSIXct(date_time_orig),month_orig=month(date_time_orig),year_orig=year(date_time_orig))]

```

## CO2 fluxes with ylim, AGC<60, and SSITC<2

```{r pressure, echo=FALSE}
# graph CO2 fluxes with a ylim
ggplot(flux2013[FC_SSITC_TEST<2 & CUSTOM_AGC_MEAN<60,], aes(date_time_orig,FC,colour=(factor(FC_SSITC_TEST))))+
  geom_point(size=0.2)+
  ylim(c(-20,20))
```

## H2O fluxes with ylim, AGC<60, and SSITC<2
```{r , echo=FALSE}
ggplot(flux2013[LE_SSITC_TEST<2 & CUSTOM_AGC_MEAN<60,], aes(date_time_orig,LE,colour=(factor(LE_SSITC_TEST))))+
  geom_point(size=0.2)+
  ylim(c(-500,1000))
```

## H2O fluxes with ylim, AGC<60, and no SSITC filter
```{r , echo=FALSE}
# graph H2O fluxes with a ylim with no quality check
ggplot(flux2013[CUSTOM_AGC_MEAN<60,], aes(date_time_orig,LE,colour=(factor(LE_SSITC_TEST))))+
  geom_point(size=0.2)+
  ylim(c(-500,1000))
```

## CO2 data with AGC<60
```{r, echo=FALSE}
# graph CO2 and H2O
ggplot(flux2013[CUSTOM_AGC_MEAN<60,], aes(date_time_orig,CO2,colour=(factor(FC_SSITC_TEST))))+
  geom_point()
```

## H2O data with AGC<60
```{r, echo=FALSE}
ggplot(flux2013[CUSTOM_AGC_MEAN<60,], aes(date_time_orig,H2O,colour=(factor(LE_SSITC_TEST))))+
  geom_point()
```

## Zoom in to months on H2O: April
```{r, echo=FALSE}
# zoom in to July
ggplot(flux2013[month(date_time_orig)==4 & CUSTOM_AGC_MEAN<60,], aes(date_time_orig,H2O,colour=(factor(LE_SSITC_TEST))))+
  geom_point()
```
## Raw data for April 1
```{r, echo=FALSE, include=FALSE}
ec_files <- list.files(path="/Volumes/SEL_Data_Archive/Research Data/Desert/Jornada/Bahada/Tower/EddyCovariance_ts/2013/Raw_Data/ASCII", full.names=TRUE) 
# read files and bind them into one file. fill=TRUE because of the missing columns in 2011

# coulmn names for 2013
ec1 <- do.call("rbind", lapply(ec_files[91], header = FALSE, fread, sep=",", skip = 4,fill=TRUE,
                               na.strings=c(-9999,"#NAME?"),
                               col.names=c("TIMESTAMP",
                                           "RECORD",
                                           "Ux",	"Uy",	"Uz",	"Ts",	"CO2",	"H2O",
                                           "fw",	"press",	"diag_csat","agc","t_hmp",	"e_hmp",
                                           "atm_press")))

```


```{r, echo=FALSE}
ggplot(ec1[agc<60], aes(TIMESTAMP, H2O))+
  geom_line(size=0.1)
```

## Zoom in to months on H2O: July
```{r, echo=FALSE}
# zoom in to July
ggplot(flux2013[month(date_time_orig)==7 & CUSTOM_AGC_MEAN<60,], aes(date_time_orig,H2O,colour=(factor(LE_SSITC_TEST))))+
  geom_point()
```

## Raw data for July 22
```{r, echo=FALSE, include=FALSE}
#ec_files <- list.files(path="/Volumes/SEL_Data_Archive/Research Data/Desert/Jornada/Bahada/Tower/EddyCovariance_ts/2013/Raw_Data/ASCII", full.names=TRUE) 
# read files and bind them into one file. fill=TRUE because of the missing columns in 2011

# coulmn names for 2013
ec2 <- do.call("rbind", lapply(ec_files[173], header = FALSE, fread, sep=",", skip = 4,fill=TRUE,
                               na.strings=c(-9999,"#NAME?"),
                               col.names=c("TIMESTAMP",
                                           "RECORD",
                                           "Ux",	"Uy",	"Uz",	"Ts",	"CO2",	"H2O",
                                           "fw",	"press",	"diag_csat","agc","t_hmp",	"e_hmp",
                                           "atm_press")))

```


```{r, echo=FALSE}
ggplot(ec2[agc<60], aes(TIMESTAMP, H2O))+
  geom_line(size=0.1)
```

## Zoom in to months on H2O: September
```{r, echo=FALSE}
# zoom in to July
ggplot(flux2013[month(date_time_orig)==9 & CUSTOM_AGC_MEAN<60,], aes(date_time_orig,H2O,colour=(factor(LE_SSITC_TEST))))+
  geom_point()
```

## Raw data for September 10
```{r, echo=FALSE, include=FALSE}
#ec_files <- list.files(path="/Volumes/SEL_Data_Archive/Research Data/Desert/Jornada/Bahada/Tower/EddyCovariance_ts/2013/Raw_Data/ASCII", full.names=TRUE) 
# read files and bind them into one file. fill=TRUE because of the missing columns in 2011

# coulmn names for 2013
ec3 <- do.call("rbind", lapply(ec_files[253], header = FALSE, fread, sep=",", skip = 4,fill=TRUE,
                               na.strings=c(-9999,"#NAME?"),
                               col.names=c("TIMESTAMP",
                                           "RECORD",
                                           "Ux",	"Uy",	"Uz",	"Ts",	"CO2",	"H2O",
                                           "fw",	"press",	"diag_csat","agc","t_hmp",	"e_hmp",
                                           "atm_press")))

```


```{r, echo=FALSE}
ggplot(ec3[agc<60], aes(TIMESTAMP, H2O))+
  geom_line(size=0.1)
```


## Raw data for September 16
```{r, echo=FALSE, include=FALSE}
#ec_files <- list.files(path="/Volumes/SEL_Data_Archive/Research Data/Desert/Jornada/Bahada/Tower/EddyCovariance_ts/2013/Raw_Data/ASCII", full.names=TRUE) 
# read files and bind them into one file. fill=TRUE because of the missing columns in 2011

# coulmn names for 2013
ec4 <- do.call("rbind", lapply(ec_files[269], header = FALSE, fread, sep=",", skip = 4,fill=TRUE,
                               na.strings=c(-9999,"#NAME?"),
                               col.names=c("TIMESTAMP",
                                           "RECORD",
                                           "Ux",	"Uy",	"Uz",	"Ts",	"CO2",	"H2O",
                                           "fw",	"press",	"diag_csat","agc","t_hmp",	"e_hmp",
                                           "atm_press")))

```


```{r, echo=FALSE}
ggplot(ec4[agc<60], aes(TIMESTAMP, H2O))+
  geom_line(size=0.1)
```

## Raw data for September 30
```{r, echo=FALSE, include=FALSE}
#ec_files <- list.files(path="/Volumes/SEL_Data_Archive/Research Data/Desert/Jornada/Bahada/Tower/EddyCovariance_ts/2013/Raw_Data/ASCII", full.names=TRUE) 
# read files and bind them into one file. fill=TRUE because of the missing columns in 2011

# coulmn names for 2013
ec4 <- do.call("rbind", lapply(ec_files[273], header = FALSE, fread, sep=",", skip = 4,fill=TRUE,
                               na.strings=c(-9999,"#NAME?"),
                               col.names=c("TIMESTAMP",
                                           "RECORD",
                                           "Ux",	"Uy",	"Uz",	"Ts",	"CO2",	"H2O",
                                           "fw",	"press",	"diag_csat","agc","t_hmp",	"e_hmp",
                                           "atm_press")))

```


```{r, echo=FALSE}
ggplot(ec4[agc<60], aes(TIMESTAMP, H2O))+
  geom_line(size=0.1)
```


## Zoom in to months on H2O: October
```{r, echo=FALSE}
# zoom in to July
ggplot(flux2013[month(date_time_orig)==10 & CUSTOM_AGC_MEAN<60,], aes(date_time_orig,H2O,colour=(factor(LE_SSITC_TEST))))+
  geom_point()
```

## Raw data for October 8
```{r, echo=FALSE, include=FALSE}
#ec_files <- list.files(path="/Volumes/SEL_Data_Archive/Research Data/Desert/Jornada/Bahada/Tower/EddyCovariance_ts/2013/Raw_Data/ASCII", full.names=TRUE) 
# read files and bind them into one file. fill=TRUE because of the missing columns in 2011

# coulmn names for 2013
ec5 <- do.call("rbind", lapply(ec_files[281], header = FALSE, fread, sep=",", skip = 4,fill=TRUE,
                               na.strings=c(-9999,"#NAME?"),
                               col.names=c("TIMESTAMP",
                                           "RECORD",
                                           "Ux",	"Uy",	"Uz",	"Ts",	"CO2",	"H2O",
                                           "fw",	"press",	"diag_csat","agc","t_hmp",	"e_hmp",
                                           "atm_press")))

```


```{r, echo=FALSE}
ggplot(ec5[agc<60], aes(TIMESTAMP, H2O))+
  geom_line(size=0.1)
```

```{r, echo=FALSE}

p1.co2 <- ggplot(flux2013[CUSTOM_AGC_MEAN<60,], aes(date_time_orig,CO2,colour=(factor(FC_SSITC_TEST))))+
  geom_point(size=0.2)+
  ylim(c(300,500))

p1.h2o <- ggplot(flux2013[CUSTOM_AGC_MEAN<60,], aes(date_time_orig,H2O,colour=(factor(LE_SSITC_TEST))))+
  geom_point(size=0.2)

p1.rain <- ggplot(flux2013, aes(date_time_orig,P_RAIN_1_1_1))+
  geom_line()

p1.rh <- ggplot(flux2013, aes(date_time_orig,RH_1_1_1))+
  geom_line()

p1.ta <- ggplot(flux2013, aes(date_time_orig,TA_1_1_1))+
  geom_line()

plot_grid(p1.co2+theme(axis.text.x = element_blank(),
                      axis.title.x = element_blank(),
                      legend.position ="none"),
          p1.h2o+theme(axis.text.x = element_blank(),
                      axis.title.x = element_blank(),
                      legend.position ="none"),
          p1.rain+theme(axis.text.x = element_blank(),
                      axis.title.x = element_blank()),
          p1.rh+theme(axis.text.x = element_blank(),
                      axis.title.x = element_blank(),
                      legend.position ="none"),
          p1.ta,
          nrow=5,
          align="v")
```


## Look at data from Eddy Pro with No absolute limits processing
```{r cars, include=FALSE, echo=FALSE}
# EddyPro 7.0.4 has column name slip problems, using Fluxnet output!

# Fluxnet output is hanging when reading in when encountering lines with
# not_enough_data
# read full output instead
flux2013nl.names <- colnames(fread("/Volumes/SEL_Data_Archive/Research Data/Desert/Jornada/Bahada/Tower/EddyCovariance_ts/2013/EddyPro_Out_TestProcessingParameters/eddypro_JER_2013_NoLimits_full_output_2022-11-08T210631_adv.csv",
                  sep=",", header=TRUE, na.strings=c("-9999"),skip=1)[1,])

flux2013nl.units <- fread("/Volumes/SEL_Data_Archive/Research Data/Desert/Jornada/Bahada/Tower/EddyCovariance_ts/2013/EddyPro_Out_TestProcessingParameters/eddypro_JER_2013_NoLimits_full_output_2022-11-08T210631_adv.csv",
                  sep=",", header=TRUE, na.strings=c("-9999"),skip=1)[1:2,]


flux2013nl <- fread("/Volumes/SEL_Data_Archive/Research Data/Desert/Jornada/Bahada/Tower/EddyCovariance_ts/2013/EddyPro_Out_TestProcessingParameters/eddypro_JER_2013_NoLimits_full_output_2022-11-08T210631_adv.csv",
                  sep=",", header=FALSE, na.strings=c("-9999"),skip=3,col.names=flux2013nl.names)

# remove duplicate data
flux2013nl <- (flux2013nl[!(duplicated(flux2013nl, by=c("date","time")))])

# make sure the data are ordered:
flux2013nl <- flux2013nl[order(date,time),]

# format date
flux2013nl[,':=' (date_time_orig = ymd_hm(paste(date,time)))][
  ,':='(date_orig=as.Date.POSIXct(date_time_orig),month_orig=month(date_time_orig),year_orig=year(date_time_orig))]

#import biomet
flux2013nl.b.names <- colnames(fread("/Volumes/SEL_Data_Archive/Research Data/Desert/Jornada/Bahada/Tower/EddyCovariance_ts/2013/EddyPro_Out_TestProcessingParameters/eddypro_JER_2013_NoLimits_biomet_2022-11-08T210631_adv.csv",
                  sep=",", header=TRUE, na.strings=c("-9999"))[1,])


flux2013nl.b <- fread("/Volumes/SEL_Data_Archive/Research Data/Desert/Jornada/Bahada/Tower/EddyCovariance_ts/2013/EddyPro_Out_TestProcessingParameters/eddypro_JER_2013_NoLimits_biomet_2022-11-08T210631_adv.csv",
                  sep=",", header=FALSE, na.strings=c("-9999"),skip=2,col.names=flux2013nl.b.names)

# format date
flux2013nl.b[,':=' (date_time_orig = ymd_hm(paste(date,time)))][
  ,':='(date_orig=as.Date.POSIXct(date_time_orig),month_orig=month(date_time_orig),year_orig=year(date_time_orig))]


```
## CO2 fluxes with ylim, AGC<60, and SSITC<2

```{r pressure, echo=FALSE}
# graph CO2 fluxes with a ylim
ggplot(flux2013nl[qc_co2_flux<2 & agc_mean<60,], aes(date_time_orig,co2_flux,colour=(factor(qc_co2_flux))))+
  geom_point(size=0.2)+
  ylim(c(-20,20))
```

## H2O fluxes with ylim, AGC<60, and SSITC<2
```{r , echo=FALSE}
ggplot(flux2013nl[qc_h2o_flux<2 & agc_mean<60,], aes(date_time_orig,LE,colour=(factor(qc_h2o_flux))))+
  geom_point(size=0.2)+
  ylim(c(-500,3000))
```

## H2O fluxes with ylim, AGC<60, and no SSITC filter
```{r , echo=FALSE}
# graph H2O fluxes with a ylim with no quality check
ggplot(flux2013nl[agc_mean<60,], aes(date_time_orig,LE,colour=(factor(qc_h2o_flux))))+
  geom_point(size=0.2)+
  ylim(c(-500,3000))
```

## CO2 µmol+1mol_a-1 data with AGC<60
```{r, echo=FALSE}
# graph CO2 and H2O
ggplot(flux2013nl[qc_co2_flux<2 & agc_mean<60,], aes(date_time_orig,co2_mole_fraction,colour=(factor(qc_co2_flux))))+
  geom_point(size=0.2)+
  ylim(c(300,500))
```

## H2O µmol+1mol_a-1 data with AGC<60, CO2 mole fraction, Prain, and RH
```{r, echo=FALSE}

p.co2 <- ggplot(flux2013nl[qc_co2_flux<2 & agc_mean<60,], aes(date_time_orig,co2_mole_fraction,colour=(factor(qc_co2_flux))))+
  geom_point(size=0.2)+
  ylim(c(300,500))

p.h2o <- ggplot(flux2013nl[qc_h2o_flux<2 & agc_mean<60,], aes(date_time_orig,h2o_mole_fraction,colour=(factor(qc_h2o_flux))))+
  geom_point(size=0.2)

p.rain <- ggplot(flux2013nl.b, aes(date_time_orig,P_rain_1_1_1))+
  geom_line()

p.rh <- ggplot(flux2013nl.b, aes(date_time_orig,RH_1_1_1))+
  geom_line()

plot_grid(p.co2+theme(axis.text.x = element_blank(),
                      axis.title.x = element_blank(),
                      legend.position ="none"),
          p.h2o+theme(axis.text.x = element_blank(),
                      axis.title.x = element_blank(),
                      legend.position ="none"),
          p.rain+theme(axis.text.x = element_blank(),
                      axis.title.x = element_blank()),
          p.rh,
          nrow=4,
          align="v")
```



